PCA

### 2019-12-22 analysis/02_PCA.Rmd
all and tissue specific figs
new pca images

g <- fviz_screeplot(charfviz, addlabels = TRUE, ylim = c(0, 50),  ncp = 5, barcolor = "white", barfill = "white") + 
  labs(title = NULL, y = "PC Variance") + theme_B3() 
h <- fviz_pca_var(charfviz,  labelsize = 3 , axes.linetype = "blank", 
                   repel = TRUE ,
                  select.var= list(contrib = 6)) + 
      theme_B3() + 
      labs(x = "PC1", y = "PC2", title =  NULL) +
      theme( axis.text = element_blank())

@@

```{r tissuespecific, fig.height=7,fig.width=7}
h1 <- plotcolorfulpcs(hyppca, hyppca$sex, sexcolors) 
h2 <- plotcolorfulpcs(hyppca, hyppca$treatment, colorscharmaip)

@@

@@

  p1 <- fviz_contrib(frizdf, choice = "var", 
                     axes = 1, top = 3 , sort.val = "asc")  + 
    labs(title = NULL,   x = "PC1", y = NULL) + 
    theme_B3() + coord_flip() +
    theme(axis.text.x = element_blank())

  p2 <- fviz_contrib(frizdf, choice = "var", 
                     axes = 2, top = 3 , sort.val = "asc")  + 
    labs(title = NULL,   x = "PC2", y = "contrib.") + 
     theme_B3()  + coord_flip() +
    theme(axis.text.x = element_blank())

  p3 <- plot_grid(p1,p2, align = "v", nrow = 2, rel_heights = c(1,1.2))
  print(p3)
}

h3 <- plotfriz(hypv) 
p3 <-plotfriz(pitfviz)
g3 <- plotfriz(gonfviz)

h4 <- plotcolorfultsnes(hyptsne, hyptsne$sex, sexcolors)   
h5 <- plotcolorfultsnes(hyptsne, hyptsne$treatment, colorscharmaip)

p4 <- plotcolorfultsnes(pittsne, pittsne$sex, sexcolors)   
p5 <- plotcolorfultsnes(pittsne, pittsne$treatment, colorscharmaip)

g4 <- plotcolorfultsnes(gontsne, gontsne$sex, sexcolors)   
g5 <- plotcolorfultsnes(gontsne, gontsne$treatment, colorscharmaip)

plot_grid(h4,h5,h2,h3,
          p4,p5,p2,p3,
          g4,g5,g2,g3,
          nrow = 3,
          labels = "auto", label_size = 10)

>>>>

g <- fviz_screeplot(charfviz, addlabels = TRUE, ylim = c(0, 50),  ncp = 5, barcolor = "white", barfill = "white") + 
  labs(title = NULL, y = "PC Variance") + theme_B3() 
h <- fviz_pca_var(charfviz,  labelsize = 3 , axes.linetype = "blank", 
                   repel = TRUE ,
                  select.var= list(contrib = 5)) + 
      theme_B3() + 
      labs(x = "PC1 (35.8%)", y = "PC2 (32.5%)", title =  NULL) +
      theme( axis.text = element_blank())

@@

```{r tissuespecific, fig.height=7,fig.width=7}

## tsne 
h4 <- plotcolorfultsnes(hyptsne, hyptsne$sex, sexcolors)  + labs(y = "hypothalamus") 
h5 <- plotcolorfultsnes(hyptsne, hyptsne$treatment, colorscharmaip)

p4 <- plotcolorfultsnes(pittsne, pittsne$sex, sexcolors)   + labs(y = "pituitary") 
p5 <- plotcolorfultsnes(pittsne, pittsne$treatment, colorscharmaip)

g4 <- plotcolorfultsnes(gontsne, gontsne$sex, sexcolors)  + labs(y = "gonads")  
g5 <- plotcolorfultsnes(gontsne, gontsne$treatment, colorscharmaip)

## pca

h1 <- plotcolorfulpcs(hyppca, hyppca$sex, sexcolors) 
h2 <- plotcolorfulpcs(hyppca, hyppca$treatment, colorscharmaip)

@@

# screeplot for variance
fviz_screeplot(hypv, addlabels = TRUE,   ncp = 5) + 
  labs(title = NULL, y = "PC Variance") + theme_B3() 
fviz_screeplot(pitfviz, addlabels = TRUE,   ncp = 5) + 
  labs(title = NULL, y = "PC Variance") + theme_B3() 
fviz_screeplot(gonfviz, addlabels = TRUE,    ncp = 5) + 
  labs(title = NULL, y = "PC Variance") + theme_B3()

# fviz contributions

@@

     p <- fviz_pca_var(frizdf,  labelsize = 3.5 , axes.linetype = "blank", 
                   repel = T ,  select.var= list(contrib = 3))  + 
      labs(title = NULL) + 
      theme_B3() + 
      theme(axis.text = element_blank())
   print(p)
}

h3 <- plotfriz(hypv) + labs(x = "PC1 (59.8%)", y = "PC2 (37.7%)") 
p3 <-plotfriz(pitfviz) + labs(x = "PC1 (54.3%)", y = "PC2 (35.7%)") 
g3 <- plotfriz(gonfviz) + labs(x = "PC1 (82.7%)", y = "PC2 (11.6%)")

## all together now

plot_grid(h4,h5,h2,h3,
          p4,p5,p2,p3,
          g4,g5,g2,g3,
          nrow = 3,
          labels = "auto", label_size = 10)
```
